---
title: "Task2-Finding optimal no. of clusters using unsupervised learning"
output: html_document
---

Importing Required libraries:

```{r}
library(cluster.datasets)
library(tidyverse)
library(gridExtra)
library(cluster)
library(factoextra)
library(GGally)
library(plotly)
```

Reading and checking data :
```{r}
data <- read.csv("Iris.csv")
head(data)
```
 
 Visualising data w.r.t every attribute.
 
```{r}
plot1 <- data %>% 
  ggplot(aes(x = Species, y = SepalLengthCm)) + 
  geom_jitter(width = .025, height = 0, size = 2, alpha = .5, color = "blue") +
  labs(x = "", y="Sepal Lenght")


plot2 <-  data %>%
  ggplot(aes(x = Species, y = SepalWidthCm)) + 
  geom_jitter(width = .02, height = 0, size = 2, alpha = .6,  color = "orange") +
  labs(x = "", y="Sepal Width")

plot3 <-  data %>%
  ggplot(aes(x = Species, y = PetalLengthCm)) + 
  geom_jitter(width = .02, height = 0, size = 2, alpha = .6,  color = "green") +
  labs(x = "", y="petal length")

plot4 <-  data %>%
  ggplot(aes(x = Species, y = PetalWidthCm)) + 
  geom_jitter(width = .02, height = 0, size = 2, alpha = .6,  color = "red") +
  labs(x = "", y="petal width")

grid.arrange(plot1, plot2, plot3, plot4)
```

Using Kmeans, lets take k=3.

```{r}
set.seed(23)
input <- data[,2:5]
clustering <- kmeans(input, centers = 3, nstart = 20)
clustering
```

With these, 3 clusters are formed with sizes 50,38 and 62 and (between_SS / total_SS =  88.4 %) which is good but lets check further.

```{r}
wssplot <- function(data, nc=15, seed=123){
  wss <- (nrow(data)-1)*sum(apply(data,2,var))
  for (i in 2:nc){
    set.seed(seed)
    wss[i] <- sum(kmeans(data, centers=i)$withinss)}
  plot(1:nc, wss, type="b", xlab="Number of groups",
       ylab="Sum of squares within a group")}

wssplot(input, nc = 20)
```
By Analysing the chart from right to left, we can see that when the number of groups (K) reduces from 3 to 2 there is a big increase in the sum of squares, bigger than any other previous increase. That means that when it passes from 3 to 2 groups there is a reduction in the clustering compactness (by compactness, I mean the similarity within a group).


Lets use Silhouette coefficient to evaluate goodness of clustering.
Silhouette Method:

```{r}
sil <- silhouette(clustering$cluster, dist(input))
```

The silhouette plot below gives us evidence that our clustering using 3 groups is good because there’s no negative silhouette width and most of the values are bigger than 0.5.

```{r}
fviz_silhouette(sil)
```

```{r}
data$cluster <- as.factor(clustering$cluster)
data
```

```{r}
ggplot(data)+
  geom_point(aes(Id,SepalLengthCm,col = "Species"))
p <- ggparcoord(data = data, columns = c(2:5), groupColumn = "cluster", scale = "std") + labs(x = "Iris Properties", y = "value (in standard-deviation units)", title = "Clustering")
ggplotly(p)
```

As we can see in the plot above, observations within the same group tend to have similar characteristics.
So from analysis these is safe to say the optimal no.of clusters for the given data is 3.
