---
title: "Task1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
data <- read.csv("task1.csv")
head(data)
```


#Lets visualize the data to get an better understanding...
1. Scatter Plot
```{r }
ggplot(data,aes(Hours,Scores))+
  geom_point()
```

2. Smooth & Line plot
```{r}
 ggplot(data,aes(Hours,Scores))+
  geom_line()+
  geom_smooth()

```

From above two graph it is pretty clear that the relationship between the Hours and Scores is positive.
Now lets check if there are any outliers, for that we will create boxplot.

3. Boxplot

```{r }
ggplot(data)+
  geom_boxplot(aes("",Hours))
```

```{r }
ggplot(data)+
  geom_boxplot(aes("",Scores))
```

From the boxplots above we can see there are no outliers present.

We have seen the relationship between the variables using visualization, Now lets see it numerically...

```{r}
cor(data$Hours,data$Scores)
```
#cor() provide us with correlational value...which in our case is 0.9761907
#which is pretty high and which shows a positive relationship.

Now that we have seen the relationship numerically and graphically...Lets build an linear model.
Create Training and Test data -

```{r}
set.seed(123)
trainingRowIndex <- sample(1:nrow(data), 0.7*nrow(data))  # row indices for training data
trainingData <- data[trainingRowIndex, ]  # model training data
testData  <- data[-trainingRowIndex, ]   # test data
```

```{r}
lmMod <- lm(Scores ~ Hours, data=trainingData)  # build the model
scorePred <- predict(lmMod, testData)  # predict score
summary(lmMod)
```

```{r}
actuals_preds <- data.frame(cbind(actuals=testData$Scores, predicteds=scorePred))  # make actuals_predicteds dataframe.
correlation_accuracy <- cor(actuals_preds)
correlation_accuracy
```

```{r}
head(actuals_preds)
```

Min-Max Accuracy Calculation
```{r}
min_max_accuracy <- mean(apply(actuals_preds, 1, min) / apply(actuals_preds, 1, max))  
min_max_accuracy
```
# So the min-max accuracy is 90%, which is pretty good. 

Mean absolute percentage deviation Calculation
```{r}
mape <- mean(abs((actuals_preds$predicteds - actuals_preds$actuals))/actuals_preds$actuals)
mape
```
#And the Mean absolute percentage deviation is 11%.

Now here we have the measure of accuracy which is at 90%, which is high and 
mean absolute predcition deviation is 11.8%, which is low,
And this shows our model is prediction is goog enough.


And now to find the answer for the question, What will be predicted score if a student studies for 9.25 hrs/ day?
            
```{r}
hour <- data.frame(Hours = 9.25)
predict(lmMod,hour)
```
 
So according to my prrdiciton when a student studies for 9.25 hours/day he might get 95.42%.